%!TEX root = ../main.tex

\chapter*{Acknowledgements}
The past several years of research, writing, and occasional despair, have changed who I am forever.
So many have helped or advised me during this time that it is difficult for me to even begin to acknowledge them all.
Any thanks I can give is too little  recompense for what many have given me.

I would like to thank my Ph.D. advisor, Professor Joemon Jose, for his continued help and advice, and for giving me the opportunity to ride the roller-coaster that has been my Ph.D.
The journey has had its ups and its downs, and I am grateful for his guidance that  helped me reach the end.

I will always have fond memories thanks to the people I worked beside, and I will forever be in their debt;
I do not believe I would have completed this work without their help and support.
To Adam, Colin, David, Fajie, Felix, Jesus, Jorge, Kim, Phil, Rami, Stewart, Stuart, and Yashar: Thank You.

I would like to thank my examiners, Nirmalie Wiratunga and Jeff Dalton, both of whom gave excellent feedback and fair criticism where it was due, which contributed greatly to the final version of this thesis.

I must thank my family and friends who have given me continued help and support over the years.
In particular, I owe eternal gratitude to my mother, who has encouraged me at every step in life.
I cannot begin to thank my (now) wife Megan, for not only putting up with me while I worked towards my Ph.D, but for being a constant support without which I do not know how I would have coped.

